Challenges to the Two-Infall Scenario by Large Stellar Age Catalogs

### 2025-07-03 src/tex/ms.tex

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{src/tex/figures/ofe_distribution_params.pdf}
    \caption{Normalized stellar [O/Fe] distributions predicted by multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). 
    % The layout is similar to Figure \ref{fig:ofe-distribution-yields}. 
    Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right, and the vertical scale is consistent across each row. Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn. The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}). For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
    Each column shows the distributions predicted from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$
    % (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); 
    {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$. {\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
    \label{fig:ofe-distribution-parameters}
\end{figure*}

@@

Next, in model (c) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times. We choose this value because if it were any higher, the infalling gas would have higher metallicity than the most metal-poor thin disk stars. This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case. We assume that the infalling gas has $\mathOFe=0$ at all times; an alternate run with $\mathOFe=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations. 
% In summary, pre-enriched gas infall may be necessary for the two-infall model to match the observed [O/Fe] distribution across the disk.

Finally, in model (d) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$. This value means that 1 in 3 stars in the Solar annulus belong to the thick disk and is on the high end of estimates (see Section \ref{sec:sfh}). The result as shown in Figure \ref{fig:ofe-distribution-parameters} is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the previous models. In summary, either pre-enriched infall or an enhanced disk mass ratio can improve agreement with the observed thin disk abundances for the \yZ{2} case. These parameters also help the model better fit the age--metallicity relation, as shown in Section \ref{sec:age-abundance} for the \yZ{1} case.

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{src/tex/figures/ofe_distribution_params.pdf}
    \caption{Normalized stellar [O/Fe] distributions predicted by multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). 
    % The layout is similar to Figure \ref{fig:ofe-distribution-yields}. 
    Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right, and the vertical scale is consistent across each row. Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn. The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}). For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex.
    Each column shows the distributions predicted from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$
    % (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); 
    {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$; and {\bf (d)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$. {\bf Key takeaway:} For the \yZ{2} case, a higher thick-to-thin disk ratio or pre-enrichment of the accreted gas can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
    \label{fig:ofe-distribution-parameters}
\end{figure*}

@@

Next, in model (c) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$. This value means that 1 in 3 stars in the Solar annulus belong to the thick disk and is on the high end of estimates (see Section \ref{sec:sfh}). The result as shown in Figure \ref{fig:ofe-distribution-parameters} is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the other models.

Finally, in model (d) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times. We choose this value because if it were any higher, the infalling gas would have higher metallicity than the most metal-poor thin disk stars. This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case. We assume that the infalling gas has $\mathOFe=0$ at all times; an alternate run with $\mathOFe=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations. In summary, either an enhanced disk mass ratio or pre-enriched infall can improve agreement with the observed thin disk abundances for the \yZ{2} case. These parameters also help the model better fit the age--metallicity relation, as shown in Section \ref{sec:age-abundance} for the \yZ{1} case.
